\documentclass{article}
\usepackage{booktabs}
\usepackage{geometry}
\usepackage{indentfirst}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }
\usepackage[utf8]{vietnam}

\title{Session 1: English and Social Sciences}
\author{Linh}
\date{06/04/2023}
\begin{document}
    \maketitle
    \section{English: Reading skill}
    \begin{itemize}
        \item Skim over and watch for the answers
        \item Watch your time
        \item Underline!
        \item Unfamiliar vocabulary? That's OK!
        \item Cross out the wrong answers
    \end{itemize}

    Practice exercise 1: \texttt{https://ielts-up.com/reading/true-false-not-given-1.html}
    
    Practice exericse 2: \texttt{https://ielts-up.com/reading/multiple-choice-1.html}
    \section{History: Cold War}
    Article to read: \texttt{https://luatminhkhue.vn/chien-tranh-lanh-la-gi.aspx}

    Questions for food thoughts:
    \begin{itemize}
        \item What is the Cold War?
        \item Why it happened?
        \item The purpose of it?
    \end{itemize}
    \section{Geography: VN Soil}
    Map to analogize: \texttt{https://vietnam.opendevelopmentmekong.net/vi/layers/tieng-viet-tho-nhuong/}

    Article to read: \texttt{https://luatduonggia.vn/tho-nhuong-la-gi-dac-diem-va-yeu-to-hinh-thanh-tho-nhuong/}
    \begin{itemize}
        \item Thổ nhưỡng là gì?
        \item Các nhân tố hình thành thổ nhưỡng?
        \item Ba nhóm đất chính của Việt Nam?
        \item Nhìn bản đồ, quan sát và hình dung phân bố của đất, nhóm đất chính của từng vùng miền?
    \end{itemize}
    \section{Reflect!}
    Practice the understanding with Quizizz: \texttt{https://quizizz.com/join?gc=05709455}
    \end{document}