\documentclass{article}
\usepackage{booktabs}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{indentfirst}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }
\usepackage[utf8]{vietnam}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }

\urlstyle{same}
\title{Session 2: Biology and Physics}
\author{Linh}
\date{08/04/2023}
\begin{document}
    \maketitle
    \section{Biology: Evolution}

    Watching List:

    \begin{itemize}
    \item \href{https://youtu.be/mZt1Gn0R22Q}{Myths and misconceptions about evolution - Alex Gendler}
    \item (Bonus) \href{https://youtu.be/vcPJkz-D5II}{The evolution of animal genitalia - Menno Schilthuizen}
    \end{itemize}
    
    Food for thoughts, maybe need research more outside the video:
    
    \begin{itemize}
        \item What is revolution?
        \item How is it actually happen?
        \item Explain the concept of "natural selection"?
    \end{itemize}

    \section{Physics: What is Physics?}

    Watching List:

    \begin{itemize}
        \item \href{https://youtu.be/ZihywtixUYo}{The Map of Physics}
        \item \href{https://youtu.be/Q_h4IoPJXZw}{What is the Wave/Particle Duality? Part 1}
        \item \href{https://youtu.be/_riIY-v2Ym8}{The Wave/Particle Duality - Part 2}
    \end{itemize}

    Food for thoughts:

    \begin{itemize}
        \item List some fields of Physics?
        \item What is Heisenberg Uncertainty Principle?
        \end{itemize}
    
    \section{Reflect!}
    
    Join the Quizizz: \texttt{https://quizizz.com/join?gc=12948367}
    \end{document}