\documentclass{beamer}
\usetheme{Copenhagen}

\title{POLYGON Project: Session 1}
\subtitle{English 1}
\author{Linh}
\date{2023-04-06}

\begin{document}

\frame{\titlepage}
\begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents
    \end{frame}
    \AtBeginSubsection[]
{
  \begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents[currentsection]
  \end{frame}
}
\section{Introduction}
\begin{frame}
\frametitle{What is English?}
\begin{itemize}
    \item English is a West Germanic language that was first spoken in early medieval England.
    \item It is named after the Angles, one of the Germanic tribes that migrated to the area of Great Britain that later took their name, England.
    \item It is closely related to the Frisian languages, but its vocabulary has been significantly influenced by other Germanic languages, particularly Norse, as well as by Latin and French.
    \item It is the most commonly learned second language and is either an official or co-official language in almost 100 countries.
    \item English is the third-most-common native language in the world, after Mandarin Chinese and Spanish.
    \item It is the most commonly learned second language and is either an official or co-official language in almost 100 countries.
\end{itemize}
\end{frame}
\begin{frame}
    \frametitle{Why you have to learn English?}
    \begin{itemize}
        \item You need to graduate from high school.
        \item You need it to get into university.
        \item You need it to communicate with others when going to work. 
    \end{itemize}
    \end{frame}
\begin{frame}
    \frametitle{What you should expect after this session?}
        \begin{itemize}
            \item Have an idea in mind how to approach a reading task
            \item Have a stragety for each kind of reading questions
            \item Learn some new vocabulary
        \end{itemize}
    \end{frame}    
\begin{frame}
    \frametitle{How you can achieve that?}
        \textbf{PRACTICE, PRACTICE AND PRACTICE}
    \end{frame}
\section{TRUE, FALSE, NOT GIVEN}
\begin{frame}
    \frametitle{Ahe}
        
    \end{frame}
\end{document}